---
title: "Murders"
author: 
date: "December 19, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a report on 2010 gun murder rates obtained from FBI reports. The original data was obtained from [this Wikipedia page](https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state).

We are going to use the following library:

```{r loading-libs, message=FALSE}
library(tidyverse)
```
  
and load the data we already wrangled:

```{r}
load("rdas/murders.rda")
```


## Least populated states

```{r}
murders %>% arrange(population) %>% head()
```

## 6 Most populated states

```{r}
murders %>% arrange(desc(population)) %>% head()
```

## Total murder reported and state population plot

```{r}
murders %>% ggplot() + geom_point(aes(x = population/10^6, y = total))
```

## 6 states with lowest murder rates

```{r}
murders %>% arrange(rate) %>% head()
```

## 6 states with highest population

```{r}
murders %>% arrange(desc(rate)) %>% head()
```

## 10 states with least murder rate

```{r}
murders %>% top_n(10, rate)
```

## Higest murder rates

```{r}
murders %>% arrange(desc(rate)) %>% top_n(10)
```

## Murder rate across region

```{r}
qplot(murders$region, murders$total, geom = "boxplot")
```

## Murder rate across states

```{r}
murders %>% mutate(abb = reorder(abb, rate)) %>%   ggplot(aes(abb, rate)) +  
  geom_bar(width = 0.5, stat = "identity", color = "black") +   coord_flip()
```

## US Gun murder 2010 in log scale

```{r}
murders %>% ggplot(aes(population/10^6, total, label = abb)) +      
  geom_text(nudge_x = 0.05) +    scale_x_log10() +   scale_y_log10() +   
  xlab("Populations in millions (log scale)") +    ylab("Total number of murders (log scale)") +   
  ggtitle("US Gun Murders in 2010") + geom_point(size = 3, color ="red")
```
